%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% Tailored for Keysight Software Developer Intern (PathWave PSS)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}
\pagestyle{fancy}\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Anish Dhandore}{
\href{mailto:anish.dhandore@gmail.com}{anish.dhandore@gmail.com} \,|\, 
\href{tel:+14423854968}{+1 (442) 385-4968}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{SGS North America}
\descript{| Test Engineer - Software and Wireless}
\location{Feb~2025 -- Present \;|\; San Diego, CA}
\vspace{\topsep}
\begin{tightemize}
    \item Conduct RF testing and compliance verification for 5G/LTE devices (FCC/CE) using spectrum/network analyzers and anechoic chambers.
    \item Execute throughput, mobility, carrier aggregation, and
interoperability test plans aligned to 3GPP.
    \item Operated Keysight, Anritsu, and R\&S RF test systems (signal generators, spectrum/network analyzers, call-box/gNB emulators) to measure EVM, ACLR, SEM, spurious emissions, and receiver sensitivity.
\end{tightemize}
\sectionsep

\runsubsection{Swift Tech}
\descript{| Developer}
\location{Mar~2023 -- May~2023 \;|\; Remote}
\begin{tightemize}
  \item Built application features using React and TypeScript, integrating REST APIs and backend services for data-driven workflows.
  \item Implemented reusable components, object-oriented patterns, and state management to improve software maintainability.
  \item Added analytics instrumentation and validation hooks to support iterative refinement and usability evaluation.
\end{tightemize}
\sectionsep

\runsubsection{Google Developer Clubs}
\descript{| President}
\location{Jan~2022 -- Aug~2024 \;|\; CSUSM}
\begin{tightemize}
  \item Led workshops on Python, C++ fundamentals, and software engineering practices with focus on architecture and optimization.
  \item Coordinated cross-functional teams for projects and hackathons; facilitated design discussions and technical collaboration.
\end{tightemize}
\sectionsep

\runsubsection{CSUSM STEM Success Center}
\descript{| STEM Tutor}
\location{Aug~2021 -- Dec~2022 \;|\; San Marcos, CA}
\begin{tightemize}
  \item Tutored students in C++ programming, object-oriented design, data structures, and algorithmic problem-solving.
  \item Created structured reference materials and example solutions to reinforce software architecture concepts.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{Dance AI}
\descript{| AI-Driven Software System — \href{https://github.com/anishdhandore/Dance_AI_Cleanup}{GitHub}}
\location{2025 | World's Largest Hackathon (bolt.new) --- Prize Winner}
\begin{tightemize}
  \item Built an NLP+graphics pipeline: RoBERTa emotion classifier and SVR intensity drive real-time dance animations in a React/Three.js UI.
  \item Exposed Python backend as REST/WebSocket API; packaged with Docker; shipped an interactive Gradio demo.
\end{tightemize}
\sectionsep

\runsubsection{Soccer Match Predictions}
\descript{| Machine Learning \& Data Modeling — \href{https://colab.research.google.com/drive/1xT5S3eeZPcjfPexal9m9Z2PjLedSJ0wA?usp=sharing}{Colab}}
\location{2022}
\begin{tightemize}
 \item Built an ML pipeline on a 20-year Kaggle dataset; engineered features (home/away effects, goal differential) with robust cleaning and outlier handling; baseline linear regression achieved MAE 31.97 and RMSE 39.72.
 \item Delivered interpretable insights with Matplotlib/Seaborn and structured the notebook for easy extension with ensemble models and cross-validation.
\end{tightemize}
\sectionsep

\runsubsection{Preserving Paws}
\descript{| Django-Based Software Platform — \href{https://github.com/anishdhandore/ST-Hacks-2021}{GitHub}}
\location{2021 | ST Hacks 2021 Hackathon --- Prize Winner}
\begin{tightemize}
  \item Built a Django web application with relational database models, asynchronous workflows, and API integrations.
  \item Applied design patterns, CI/CD, and modular architecture to ensure reliability under concurrent usage.
\end{tightemize}
\sectionsep

\end{minipage}
\hfill
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\runsubsection{California State University San Marcos}
\descript{| M.S., Computer Science}
\location{Dec~2025 \;|\; San Marcos, CA}
\sectionsep
\runsubsection{California State University San Marcos}
\descript{| B.S., Computer Science}
\location{Dec~2023 \;|\; San Marcos, CA}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}

\subsection{Languages}
C++ 17/20 (STL) • Python 3 • TypeScript/JavaScript (ES6+) • SQL • C\# • Bash
\sectionsep

\subsection{Backend}
Node.js (Express/Fastify) • Python (FastAPI/Flask) • ASP.NET Core • REST/gRPC • WebSockets
\sectionsep

\subsection{Frontend}
React • Next.js • Redux/RTK • React Query • Tailwind CSS • Chakra UI
\sectionsep

\subsection{Databases}
PostgreSQL • MySQL • SQLite • MongoDB • Redis
\sectionsep

\subsection{Cloud/Deveops}
AWS (EC2, S3, RDS, Lambda) • Docker • GitHub Actions • Firebase • Linux
\sectionsep

\subsection{Automation}
CI/CD, Docker, Test Automation, Code Refactoring, Log Analysis
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
Advanced Algorithms, Cloud Computing, Database Systems, Machine Learning \& Statistical Learning, Operating Systems, Computer Networks; Wireless Networks \& Mobile Systems, Software Engineering (Design Patterns, Testing, CI/CD)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards}
Dean’s List (2020–2022) \\
Hackathon Wins: ST Hacks 2021; CSUSM 2022; LPL Financial 2023; World’s Largest Hackathon 2025
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}
Portfolio:// \href{https://anishdhandore.github.io/Portfolio/}{\bf anishdhandore.github.io} \\
GitHub:// \href{https://github.com/anishdhandore}{\bf anishdhandore} \\
LinkedIn:// \href{https://www.linkedin.com/in/anish-dhandore/}{\bf anish-dhandore}
\sectionsep

\end{minipage}
\end{document}
